Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-17 prob.tex
prob.tex Keep fixing small things suggested by Prof. Ortiz...

In the previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although each event is assumed to have
a probability, the exact value of $\pmeas(E)$ may not be known. If
we want to know its value, we can run $N$ independent trials. Let
$x_{i}=1$ or $0$ denote whether the event~$E$ occurs in the $i$-th
trial or not, respectively, then $\pmeas(E)$ could be approximated
to given accuracy by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
with the probability converging to one as $N$ goes to infinity, i.e.,
. This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $h$ apart. It is a known fact that
the probability of the needle crossing a line is $\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

@@

\begin{definition}{[}Ideal Measurement; Complement; Commutativity{]}~ 
\begin{itemize}
\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
an \emph{ideal measurement} if it is a partition of the identity,
i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
be mutually orthogonal~\cite{Griffiths2003}.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal
to $P$, and corresponds to the complement event~$\Omega\backslash E$
in classical probability~\cite{Griffiths2003}. 
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum,Griffiths2003}. 
\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
\end{itemize}
\qed\end{definition}

@@

\begin{example}{[}Quantum three-value interval-valued probability
measure{]} We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$, we can define
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
and $\iota\left(\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i=1}^{N}}\sum\iota\left(x_{i}\right)$,
where $x$ and $\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

>>>>

In the previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although each event is assumed to have
a probability, the exact value of $\pmeas(E)$ may not be known. If
we want to know its value, we can run $N$ independent trials. Let
$x_{i}=1$ or $0$ denote whether the event~$E$ occurs in the $i$-th
trial or not, respectively, then $\pmeas(E)$ could be approximated
to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
with the probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N}x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $h$ apart, where $\ell<h$. It is
a known fact that the probability of the needle crossing a line is
$\frac{2\ell}{\pi h}$~\cite{Buffon1777,DeMorgan1872,Hall1873,Uspensky1937}.
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
\begin{itemize}
\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
an \emph{ideal measurement} if it is a partition of the identity,
i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
be mutually orthogonal~\cite{Griffiths2003}.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal
to $P$, and corresponds to the complement event~$\Omega\backslash E$
in classical probability~\cite{Griffiths2003}. 
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum,Griffiths2003}. 
\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
\end{itemize}
\qed\end{definition}

@@

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$, we can define
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
and $\iota\left(\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\iota\left(x_{i}\right)$,
where $x$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}
